\documentclass[a4paper, 10pt]{article}
\usepackage[margin=2.2cm]{geometry}
\usepackage{plex-otf}
\usepackage{enumitem}

\setlength{\parskip}{0pt} 
\setlength{\parindent}{0pt}

\newcommand{\mytitle}{Essay Outline}
\newcommand{\theauthor}{Rivo Juicer Wowor}
\newcommand{\affiliation}{00000059635}

\usepackage{fancyhdr}
\fancypagestyle{plain}{
  \fancyhf{}
  \lhead{\footnotesize{\textbf{\mytitle}}}
  \fancyfoot[R]{\thepage}
  \fancyfoot[L]{\footnotesize{\theauthor \hspace{1pt} (\affiliation)}}
  \renewcommand{\headrulewidth}{0pt}% Line at the header invisible
  \renewcommand{\footrulewidth}{0.4pt}% Footer line not visible with 0pt
}

\pagestyle{plain}

\begin{document}
    \section*{Introduction}
    \subsection*{Background}
        Linux have the lowest desktop market share in the world.
    \subsection*{Main Idea}
        Linux should be used more on the desktop, especially for beginner programmers
        in the computer science major.  

    \section*{Body Paragraph 1}
        Linux is a reliable and secure OS, because it's open-source nature.
        \subsection*{Details}
        \begin{enumerate}
            \item It's free as in speech.
            \item Everybody can contribute to fix issues without waiting for maintainers to fix.
            \item Full control on OS updates.
        \end{enumerate}

    \section*{Body Paragraph 2}
        Linux has a more flexible environment for developing software.
        \subsection*{Details}
        \begin{enumerate}
            \item Broad community of developers.
            \item Almost all development tools already available on Linux.
            \item More customizable to fit user's need.
            \item It has powerful scripting tools called \emph{Bash}.
        \end{enumerate}

    \section*{Body Paragraph 3}
        Linux is lighter than other competing OSes (OSX and Windows).
        \subsection*{Details}
        \begin{enumerate}
            \item CPU and Memory usage is significantly lower.
            \item Less bloatware and unnecessary.
            \item Can basically run almost anywhere.
        \end{enumerate}

    \section*{Conclusion}
        Linux is a better OS for developers, especially for young programmers. It is reliable,
        more secure, and even lighter to run. It also has more flexible environment for developing software.
        That's why many developers using Linux to be their main Operating System to daily drive.

\end{document}